\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex

\section{Preliminaries and Problem Statement}

In this section we describe the multi-arm bandit problem and the formal definition of our problem.

\subsection{Multi-Arm Bandit Problem}
The multi-arm bandit problem originally described by Robbins \cite{robbins1952some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and tries to infer which one will yield the highest reward.
A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1952some}, \cite{bergemann2006bandit}.

>>>>

\section{Multi-Arm Bandit Problem}
The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and tries to infer which one will yield the highest reward.
A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1952some}, \cite{bergemann2006bandit}.
